Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-01-11 doc/HH4b_Documentation.tex
Added sample runcards to documentation

\section{Samples}

@@

>>>>

\section{Samples}
\subsection{Background}
All background samples are generated with the {\tt SHERPA} event generator, version 2.1.1. For the explicit runcards used in the generation, see Appendix~\ref{app:runcards}.

The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples. At the generator level the following basic cuts are applied. Each final state particle must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$. Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ (in hindsight, $H_T/4$ would probably have made more sense).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\appendix
\section{Event sample runcards}
\label{app:runcards}
\subsection {Background: QCD 4b}
\begin{verbatim}
(run){
  EVENTS 3M;
  EVENT_GENERATION_MODE U;
  ME_SIGNAL_GENERATOR Comix;

  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4b];

  BEAM_1 2212; BEAM_ENERGY_1 7000;
  BEAM_2 2212; BEAM_ENERGY_2 7000;

  FRAGMENTATION=Off # disable hadronisation
  MI_HANDLER=None # disable multiple parton interactions

  SCF:=1; ### default scale factor
  SCALES VAR{SCF*H_T2/2};

  PDF_LIBRARY LHAPDFSherpa;
  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
  PDF_SET_VERSION 0;

  MASSIVE[5] 1;
  MASS[5] 4.75;

}(run);
(processes){
  Process 93 93 -> 5 -5 5 -5;
  Order_EW 0;
  End process;

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3.0 3.0
  PseudoRapidity -5 -3.0 3.0
}(selector);
\end{verbatim}

\subsection {Background: QCD 2b2j}
\begin{verbatim}
(run){
  EVENTS 3M;
  EVENT_GENERATION_MODE U;
  ME_SIGNAL_GENERATOR Comix;

  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_2b2j];

  BEAM_1 2212; BEAM_ENERGY_1 7000;
  BEAM_2 2212; BEAM_ENERGY_2 7000;

  FRAGMENTATION=Off # disable hadronisation
  MI_HANDLER=None # disable multiple parton interactions

  SCF:=1; ### default scale factor
  SCALES VAR{SCF*H_T2/2};

  PDF_LIBRARY LHAPDFSherpa;
  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
  PDF_SET_VERSION 0;

  MASSIVE[5] 1;
  MASS[5] 4.75;

}(run);
(processes){
  Process 93 93 -> 93 93 5 -5;
  Order_EW 0;
  End process;

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3 3
  PseudoRapidity 5 -3 3

  PT 93 20 7000
  PseudoRapidity 93 -3 3
}(selector);
\end{verbatim}

\subsection {Background: QCD 4j}
\begin{verbatim}
(run){
  EVENTS 3M;
  EVENT_GENERATION_MODE U;
  ME_SIGNAL_GENERATOR Comix;

  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4j];

  BEAM_1 2212; BEAM_ENERGY_1 7000;
  BEAM_2 2212; BEAM_ENERGY_2 7000;

  FRAGMENTATION=Off # disable hadronisation
  MI_HANDLER=None # disable multiple parton interactions

  SCF:=1; ### default scale factor
  SCALES VAR{SCF*H_T2/2};

  PDF_LIBRARY LHAPDFSherpa;
  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
  PDF_SET_VERSION 0;

  MASSIVE[5] 1;
  MASS[5] 4.75;

}(run);
(processes){
  Process 93 93 -> 93 93 93 93;
  Order_EW 0;
  End process;

}(processes);
(selector){
  PT 93 20 7000
  PseudoRapidity 93 -3 3
}(selector);
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
